---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# BusinessObjects `r emo::ji("bar_chart")`

<!-- badges: start -->
<!-- badges: end -->

This packages is an API wrapper of the SAP Business Objects API for the R language. It allows to connect R to SAP Business Objects to automate and build multiple workflows from within R.

### Installation

You can install the latest release of this package from [Github](https://github.com/matbmeijer/JirAgileR) with the following commands in `R`:

```{r, eval=FALSE} 
if (!require("devtools")) install.packages("devtools")
devtools::install_github("matbmeijer/BusinessObjects")
```

### Current functionalities `r emo::ji("wrench")`

* Log-on to SAP Business Objects REST API: `log_on()`
* Retrieve children elements from a CMS repository folder: `get_bo_folder_ressources()`
* Retrieve details from a SAP Business Objects document ID: `get_bo_document_details()`
* Retrieve schedules from a SAP Business Objects document ID: `get_bo_document_schedules()`
* Retrieve details (frequency, parameters, etc.) of a specific schedule from a SAP Business Objects document ID: `get_bo_schedule_details()`
* Upload Microsoft Excel to the SAP Business Objects' CMS Repository: `upload_excel_to_bo()`
* Update a Microsoft Excel located in te SAP Business Objects' CMS Repository: `update_bo_excel_file()`
* Retrieve SAP Business Objects connections: `get_bo_connections()`
* Retrieve SAP Business Objects configurations: `get_bo_configuration()`
* Retrieve SAP Business Objects universes: `get_bo_universes()`
* obtain the details of a SAP Business Objects universe: `get_bo_universe_details()`
* Log-off from the SAP Business Objects REST API: `log_off()`

### Documentation

* Full R package documentation ca be found here:
[https://matbmeijer.github.io/BusinessObjects](https://matbmeijer.github.io/BusinessObjects)

* Further documentation about the SAP BusinessObjects API can be found here:
[Documentation for the WEB REST API](https://help.sap.com/viewer/58f583a7643e48cf944cf554eb961f5b/4.2/en-US/7da2e2d66f701014aaab767bb0e91070.html)

### Code of Conduct

Please note that the 'BusinessObjects' project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.

### License
This package will probably never see CRAN as SAP Business Objects is not open source. Nonetheless, all the code here follows the following licensing:
[MIT © Matthias Brenninkmeijer](https://github.com/matbmeijer/BusinessObjects/blob/master/LICENSE.md)

